\textit{Urban and building multiscale co-simulation: case study implementations on two university campuses}

### 2017-05-19 latex_reviewcomments/ReviewCommentsResponse.tex

\question 11. p. 4, Figure 2. The test explains the paths associated with the dotted vertical lines and solid lines.  Presumably the use of the latter is intended to show the co-simulation path but the use of the dashed line in the related Figure 3 is not clear.  Further, Figure 3 is quite small; at minimum, the CItySIm block with its italicized vertical text, fmilib, could be modestly larger.  
\begin{solution}
\textcolor{red}{Daren -- what was our logic behind the dotted lines?}
\end{solution}

\question 12. p. 5, lines 145-154.  The text states that “several key urban-scale weather variables are send to EnergyPlus from CitySim” but does not succinctly state how CItySIm calculates these variables.  The text might indicate why the authors consider the CitySim occupancy model to be more robust.  Finally, as a minor point of English grammar, please consider removing the comma after “urban environments” in line 150 or replacing “that” with “which.” 
\begin{solution}
\textcolor{red}{Jerome -- can you explain quickly in the text how CitySim calculated these variables and why its better than using EnergyPlus's weather file inputs?}
\end{solution}

\question 13. p. 6.  The text on this page (or, apparently, any other) does not refer to Tables 1 and 2. 
\begin{solution}
References for Table 1 and 2 are no included in the text pertaining to those variables.
\end{solution}

\question 14. p. 7, line 178.  Equation 2 lacks a view factor, as is included in Evins et al., Equation 9 and in the EnergyPlus Engineering Reference. 
\begin{solution}
% \textcolor{red}{Jerome and Daren - can you confirm the accuracy of the equations?}
That is correct -- a view factor has been added to Equation 2. 
\end{solution}

@@

\question 24. p. 12, Figure 11.  The text states Figure 11 shows differences in predicted heating consumption and notes there is a consistent offset across days in January.  Figure 11 shows hourly variations for presumably averaged days and single points for each month; in short, variations across days cannot be discerned.  Are these variations important to the comparison?  The order of the bars matches Figure 10 but disagrees with Figure 9.  The text compares co-simulation with measurement (using the latter as the reference, which seems appropriate) and shows 2\% annual difference but the numbers over the bars appear to compare co-simulation and measurement with solo simulation and show 6.5\% difference.  As in Figure 11, the numbers (not percentages) over the bars are not explained. 
\begin{solution}
\textcolor{red}{Update graphics}
\end{solution}

\question 25. p. 12, section 3.5.  The text should include a reference to the Minergie standard and the caption or image in Figure 12 should identify the STCC building. 
\begin{solution}
\textcolor{red}{Add Minergie as a reference}
\end{solution}

\question 
26. p. 13, line 308.  Please explain SIA and/or provide an appropriate reference.   
\begin{solution}
\textcolor{red}{Add SIA and explain}
\end{solution}

\question 
27. p. 13, lines 310-313.  The text states that the CItySIm model was created from a DXF file from EnergyPlus.  Was this export used solely for the STCC building or was the remainder of the Quartier Nord as shown in Figure 13 designed in Open Studio? 
\begin{solution}
No, the export from EnergyPlus included both buildings -- this fact has been clarified in the text.

% \textcolor{red}{Jerome -- any feedback on this?}
\end{solution}

@@

\question 
28. P. 13, lines 316-322.  The reference in the text for percentage changes is the EnergyPlus simulation but Figures 14 and 15 place the percentages (with opposite sign) about the solo simulations.  The text states that discrepancies between solo and co-simulations are due to differences in calculation of heating and cooling loads.  Please elaborate. 
\begin{solution}
\textcolor{red}{Confirm numbers in graphics}
\end{solution}

\question 
29. P. 14, section 3.8.  The text states that the Quartier Nord building was also simulated. This is a bit confusing because Quartier Nord previously referred to the complex.  Does the building refer to the building on the right in Figures 12 and 13 – i.e., everything except the STCC?  The text also states that differences between solo and co-simulations are small because the surroundings are sparse.  If this is the case, would one expect better agreement between solo and co-simulations for the neighboring STCC?  Also, please consider replacing “due to” with “because” in line 327. 
\begin{solution}
% \textcolor{red}{Jerome -- can you clarify this?}
It is not the 'Quartier Nord Building' that is being simulated -- it is the STCC. The text has been fixed to clarify this confusion.
\end{solution}

### 2017-05-19 latex_corrected/UMEM_CoSim.tex
addressed review item

The corresponding CitySim model was created by exporting a DXF file from
EnergyPlus, and importing it into the Graphical User Interface of CitySim.
Physical characteristics of the building were added to complete the CitySim
model. Finally, the same script as described in Section \ref{Methodology} was
used to export the model from CitySim to EnergyPlus, giving a simplified
EnergyPlus model.\\

@@

Both the CitySim and EnergyPlus engines are utilized in this case study. The
first comparison to observe is the differences between the two engines when
focused on the Quartier Nord building. When simulated in isolation, the
CitySim engine predicts a 28.6\% increase in heating load and a 44.4\%
increase in cooling load as compared to EnergyPlus. This phenomenon is due to
the differences in the way each of these engines calculates heating and
cooling loads. Use of the co-simulation process brings the engines to within
5.4\%. Figure \ref{fig:qn_eplusvscitysim_cooling} illustrates these
differences for cooling and Figure \ref{fig:qn_eplusvscitysim_heating} for
heating.

\begin{figure}[H]
\centering
\includegraphics[scale=0.55]{figures/QN_Cooling}
\caption{Quartier Nord CitySim vs. EnergyPlus Solo for Cooling}
\label{fig:qn_eplusvscitysim_cooling}
\end{figure}

\begin{figure}[H]
\centering
\includegraphics[scale=0.55]{figures/QN_Heating.pdf}
\caption{Quartier Nord CitySim vs. EnergyPlus Solo for Heating}
\label{fig:qn_eplusvscitysim_heating}
\end{figure}

\subsection{EnergyPlus co-simulation results}
The Quartier Nord building is also simulated within the solo and
cosimulation environments. When
focusing on the EnergyPlus results, a 7.5\% decrease in cooling energy is
observed, as seen in Figure
\ref{fig:qn_eplus_cosimvssolo_cooling}. A 2.8\% increase in heating energy is
observed, as seen in Figure
\ref{fig:qn_eplus_cosimvssolo_heating}. These differences are less pronounced
than the HPI and theoretical case studies due to the number and proximity of
surrounding buildings is not as large. Long wave radiation exchange in this situation 
doesn't have as large of an impact on the heating and cooling calculations.

>>>>

The corresponding CitySim model was created by exporting a DXF file from
EnergyPlus for the whole of Quartier Nord, and importing it into the Graphical User Interface of CitySim.
Physical characteristics of the building were added to complete the CitySim
model. Finally, the same script as described in Section \ref{Methodology} was
used to export the model from CitySim to EnergyPlus, giving a simplified
EnergyPlus model.\\

@@

Both the CitySim and EnergyPlus engines are utilized in this case study. The
first comparison to observe is the differences between the two engines when
focused on the STCC building. When simulated in isolation, the
CitySim engine predicts a 28.6\% increase in heating load and a 44.4\%
increase in cooling load as compared to EnergyPlus. This phenomenon is due to
the differences in the way each of these engines calculates heating and
cooling loads. Use of the co-simulation process brings the engines to within
5.4\%. Figure \ref{fig:qn_eplusvscitysim_cooling} illustrates these
differences for cooling and Figure \ref{fig:qn_eplusvscitysim_heating} for
heating.

\begin{figure}[H]
\centering
\includegraphics[scale=0.55]{figures/QN_Cooling}
\caption{STCC CitySim vs. EnergyPlus Solo for Cooling}
\label{fig:qn_eplusvscitysim_cooling}
\end{figure}

\begin{figure}[H]
\centering
\includegraphics[scale=0.55]{figures/QN_Heating.pdf}
\caption{STCC CitySim vs. EnergyPlus Solo for Heating}
\label{fig:qn_eplusvscitysim_heating}
\end{figure}

\subsection{EnergyPlus co-simulation results}
The STCC building is also simulated within the solo and
cosimulation environments. When
focusing on the EnergyPlus results, a 7.5\% decrease in cooling energy is
observed, as seen in Figure
\ref{fig:qn_eplus_cosimvssolo_cooling}. A 2.8\% increase in heating energy is
observed, as seen in Figure
\ref{fig:qn_eplus_cosimvssolo_heating}. These differences are less pronounced
than the HPI and theoretical case studies due to the number and proximity of
surrounding buildings is not as large. Long wave radiation exchange in this situation 
doesn't have as large of an impact on the heating and cooling calculations.
